Title

### 2021-05-28 paper/main.tex
First half of the Free energy definitions

>>>>

The Helmholtz free energy of adsorption of an amino acid onto a
graphene layer ($\Delta A_{ads}$) can be obtained from the difference
in free energy of the Adsorbed and Free states:

\begin{equation}
\label{eq:Adsorption}
\Delta A^{ads} = A^{near} - A^{free}
\end{equation}

Where the near and free states are defined based on the
distance between the graphene layer and the $\alpha-$carbon of the
amino acid projected onto a vector normal to the graphene layer. For a
graphene layer prepared along the XY plane, this is equivalent to the
distance along the Z--axis. This distance will be defined as the
reaction coordinate $\xi$. The cut-off ranges for the near and far
states will be defined based on the PMFs (potentials of mean force)
along $\xi$ of the amino acids, which can be found in the
supplementary materials TODO.

If the potential of mean force ($\mathrm{PMF}$) along $\xi$ has been
estimated for the discrete states $\{\xi_1, \xi_2, ..., \xi_N \}$, the
probability of a state $\xi_{j}$ can be estimated with:

\begin{equation}
\label{eq:A-from-PMF}
p(\xi_j) = \frac{e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

where $\beta$ is the thermodynamic beta ($\frac{1}{k_{B}T}$). To
estimate the probability of a state with multiple possible $\xi$
values, the numerator is replaced with a sum over the individual
values of $\xi$. In this way, the probabilities of the adsorbed and
free states can be estimated with:

\begin{equation}
\label{eq:Adsorbed}
p(A) = \frac{\sum_{j \in A} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}
\begin{equation}
\label{eq:Adsorbed}
p(F) = \frac{\sum_{j \in F} e^{-\beta~\mathrm{PMF}(\xi_j)}}{\sum_{i=1}^N e^{-\beta~\mathrm{PMF}(\xi_i)}}
\end{equation}

Knowing that the probability of a state
